\documentclass[11pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
CU Boulder Administrator\\
Regent Administrative Center, Room 1B53\\
2055 Regent Drive\\
Boulder, CO 80309-0026}
%360 Woods Hole Road MS31, Clark 223\\
%Woods Hole, MA 02543}

% opening here
\opening{To the Admissions Committee:}
\raggedright % if you like this sort of thing
\setlength{\parindent}{15pt} % if you like this sort of thing

I am happy to recommend MIDN 1/C Gregory Burgess to the Department of Mechanical Engineering at University of Colorado, Boulder. I have known Mr.~Burgess for 3 years; he was an outstanding student in my ES200 (Introduction to Systems Engineering) section covering embedded microcontrollers, C and Matlab. 

Mr.~Burgess stood out for driving his team's Pokemon video game project to develop graphics and use object-oriented techniques, Matlab classes, and GUIs. In ES200, I was also impressed by his creativity in developing a swivel turret firing ping pong balls. In EW456 (Autonomous Vehicles) and EW413 (Digital Control Engineering), he is now working with Python and ROS to develop control systems for mobile robotics use.

Our department focuses on robotics, controls, and autonomy. Since taking my class, Mr. Burgess has worked on a small autonomous vehicle with a color sensor, Hall-effect sensor, and ultrasound rangefinder. It navigated a course, avoided an obstacle, and detected ``mines'' under the course. Mr. Burgess also implemented a ship’s autopilot heading control as part of our honors linear systems class. Mr. Burgess has also been underway in USS ANNAPOLIS (SSN-760). He was part of the sonar division and stood watch under instruction as helmsman/planesman, basic sonar operator, and in fire control. This practical experience with undersea warfare could benefit navigation and controls research projects.

Mr. Burgess will be presenting research conducted during his Summer Student fellowship at WHOI at the IEEE OCEANS Conference in Seattle, WA. Our department here at USNA fully supports him in his research endeavors. Mr. Burgess is currently working on a magnetic navigation research project under CDR Paul Frontera and is being immersed in graduate-level dynamics and filtering techniques. 

Mr.~Burgess is an outstanding candidate. I believe Mr.~Burgess' strong interest in applied ocean physics and engineering, his technical abilities, and his ability to juggle the tasks thrown at him as a young naval officer show he will navigate the mechanical engineering program well. 

\closing{Very respectfully,} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}